\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{tabularx}
\setlist[itemize]{leftmargin=1.5em, topsep=2pt, itemsep=2pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Sean Zeliq Urian}} \\
    \vspace{0.5em}
    Tangerang Selatan, Banten \quad | \quad 085776776388 \quad | \quad \href{mailto:seanurian@gmail.com}{seanurian@gmail.com} \\
    \href{https://www.linkedin.com/in/seanurian}{https://www.linkedin.com/in/seanurian}
\end{center}

\vspace{1em}
\section*{WORK EXPERIENCE}

\textbf{ECOMINDO (PT. ECOMINDO SARANACIPTA)} \\
\textit{Associate Software Engineer} \hfill Jul 2024 -- Present
\begin{itemize}
    \item \textbf{Sinarmas Land - Procurement Surrounding System Project}
    \begin{itemize}
        \item Developed a streamlined and effective online procurement and tender system for Sinarmas Land.
        \item Integrated all existing processes and features from previous applications and systems, including tender processes, RAB preparation, procurement analysis, vendor management, and Purchase Order issuance.
    \end{itemize}
    \item \textbf{IFG Life - Financial Institution Pension Fund}
    \begin{itemize}
        \item Designed and implemented a financial operations dashboard within a microservices architecture, enabling streamlined management of transactional inflows and outflows.
        \item Engineered a Kafka-based data synchronization layer, ensuring reliable, real-time consistency across heterogeneous databases and decoupled services.
        \item Optimized large-scale data ingestion pipelines, significantly reducing operational latency.
    \end{itemize}
\end{itemize} \\
\textbf{PINTARNYA (PT. PINTARNYA SOLUSI TEKNOLOGI)} \\
\textit{Software Engineer} \hfill Dec 2022 -- Jun 2024
\begin{itemize}
    \item Led the successful launch of Cari Pinjaman as a Full-Stack Engineer, delivering a robust end-to-end solution.
    \item Redesigned and modernized the homepage and Cari Cuan submission flow, improving usability, performance, and engagement.
    \item Migrated Pintarnya Employer Dashboard from Cloud Run to Kubernetes, reducing GCP VM-related costs by approximately 40\%.
\end{itemize}\\
\textbf{RUANGGURU (PT. RUANG RAYA INDONESIA)} \\
\textit{Software Engineer (Front-End)} \hfill Apr 2022 -- Nov 2022
\begin{itemize}
    \item Optimized frame rendering performance on BrainAcademy and Roboguru apps, improving FPS by over 50\% on large datasets.
    \item Developed a cross-platform UI kit for SkillAcademy using Tamagui, consolidating Web, Android, and iOS into a single codebase.
    \item Integrated a push notification system for the Roboguru app to enable real-time, targeted user engagement.
\end{itemize}\\
\textit{Software Engineer Intern} \hfill Jan 2022 -- Apr 2022
\begin{itemize}
    \item Adopted front-end best practices for React and React Native, focusing on performance and maintainability.
    \item Redesigned asset management strategy, reducing the React Native bundle size to under 10MB.
    \item Led the successful release of the BrainAcademy app in Indonesia and Vietnam with localization and platform stability.
\end{itemize}\\
\textbf{ECOMINDO (PT. ECOMINDO SARANACIPTA)} \\
\textit{Junior Software Engineer} \hfill Jul 2021 -- Jan 2022
\begin{itemize}
    \item Developed multi-user tools/trivia games for an online platform using only Vanilla JS, HTML, and CSS.
    \item Successfully accommodated over 100 concurrent users during the initial launch.
\end{itemize}

\section*{ORGANIZATION}

\textbf{BIMBEL MENGEJAR UI} \\
\textit{Vice Project Officer} \hfill 2019 -- 2020
\begin{itemize}
    \item Collaborated with the PO to organize Bimbel Mengejar UI 2020.
    \item Supervised 5 team members in the Media Department for web development supporting online learning.
    \item Contributed to the success of 7+ students gaining admission to their target universities.
\end{itemize}\\
\textit{Human Resource} \hfill 2018 -- 2019
\begin{itemize}
    \item Facilitated screening and interviews for 300 prospective students.
    \item Taught Mock Tests to prepare prospective teachers.
\end{itemize}\\
\textbf{SAMABA UI} \\
\textit{Public Relations} \hfill Jul 2019 -- Sep 2019
\begin{itemize}
    \item Assisted new students with pre- and re-registration issues.
\end{itemize}

\section*{EDUCATION}

\textbf{University of Indonesia - Depok, Jawa Barat} \hfill Aug 2018 -- Jul 2022 \\
Bachelor of Computer Science; GPA: 3.5/4.0



\section*{ADDITIONAL}

\begin{tabularx}{\textwidth}{@{}lX@{}}
\textbf{Skill:} & Problem Solving, Full Stack, Frontend, Backend, SQL, Scrum, Agile Methodologies, Test Driven Development, Analytical Skill, Project Management \\
\textbf{Tech Stack:} & Typescript, Javascript, Java, React, React Native, Quarkus, Next, Gatsby, Python, Django, Django Rest, Go, Postgresql, Kafka \\
\end{tabularx}
\textbf{Achievements:}
\begin{itemize}
    \item 1st Place - Senior Competitive Programming, COMPFEST UI 2020
    \item 2nd Place - Python Computing Competition, GEOFISDAY 2.0 2021
    \item 3rd Place - Capture the Flag, Pekan Ristek FASILKOM UI 2020
    \item Participant - ICPC Jakarta 2020 (Competitive Programming)
\end{itemize}

\end{document}
